%!TEX root = ../dissertation.tex
% the acknowledgments section

\newthought{}, 

\indent I'd first like to say thank you to my Ph.D. advisor Professor Melissa Franklin without whom this project would not have been possible.  Thank you for all the opportunities that you have given me and pushing me to accomplish my very best.  Thank you for the faith that you had in me when I doubted myself and thank you for taking the long, often frustrating, hours to teach me the skills that I need to succeed.  \\

\indent Also thank you my undergraduate advisor, Professor Ashutosh Kotwal, for introducing me to the field of particle physics and giving the opportunity to advance to the place I am today.  \\

\indent Thank you Professor Matt Reece for first giving me the idea for this project.  Thank you Professor Joao Guimaraes da Costa, Professor Masahiro Morii, and Professor John Huth for all the guidance you have given me all these years at Harvard.\\

\indent Thank you Kerim Suruliz, Chris Rogan, and Matthias Saimpert.  It has been a pleasure working side-by-side with all of you on the compressed stop search.  Thank you, Kerim and Chris for all the long explanations and teaching me the knowledge necessary to perform an analysis from start to finish.  Without your tireless contributions, this analysis definitely would not have made it to publication.  \\

\indent Thank you to members of the ATLAS 3rd Generation SUSY group and the Stop Zero-Lepton Group including Walter Hopkins, Vasiliki Kouskoura, Professor Iacopo Vivarelli, Fabrizio Miano, Professor George Redlinger, Andrea Rodriguez, and Calum Macdonald.  It was a pleasure to work with you and thank you for all the support. \\

\indent Laura Jeanty, Giovanni Zevi Della Porta, Pierluigi Catastini, and William Spearman it was great fun completing various projects with you during the years and thank you for all the things that you taught me when I was a young graduate student. \\

\indent Thank you Professor Ludo Pontecorvo, Professor Enrico Pasqualucci, and Professor Roberto Ferrari.  It was a pleasure to work on the ATLAS muon spectrometer with you over these many years. Thank you Ludo for your faith in my abilities. \\

\indent Thank you my fellow graduate students and post-docs in the Harvard ATLAS group: Alex Tuna, Stefano Zambino, Tomo Lazovich, Emma Tolley, Karri DiPetrillo, Tony Tong, Stephen Chan, Julia Gonski, and Jennifer Roloff.  Thank you especially, Ann Wang for suffering through my many grammar mistakes and helping me edit this thesis. \\

\indent Thank you Lisa Cacciabaudo and Carol Davis, you two have always been great support for all Harvard Graduate students.  Thank you, Barbara Drauschke for reading almost the entirety of this thesis on such short notice. \\

\indent To all the friends who I made a long the way on this long journey, David Dodsworth, Amar Doshi, Kelsey O'Connor, Natalie Fisher, Nick Langellier, Edlyn Levine, Katya Kosheleva, Manuel Olmedo, Zach Corse, Jenna Molnar, Bijan Haney, Anna Duncan, Nicola Abraham, Michael Fenton, Duncan Leggat, Cameron Dean, Harry Moss, Rose Ardell, Emma Buchanan, Rebecca Pickles, Xanthe Hoad, Stephen Jiggins, Rob Harding, Ellis Kay, Will Madden, Chloe Gray, David Lack, Elliot Reynolds, Laura Dodd, Murdo Trail, Sarah Charley, Max Hutinet, and Oliver Lantwin, may we always have fond memories to look back upon. 

\indent My middle school teacher, Mrs. Randolf, thank you for faith in me at a time when I had very little to show for. Without your push, I may have never realized my potential. My third grade teacher, Mrs. Ryan, and my English as a second language teacher, Mrs. Estes thank you for the care and attention that you gave me when I first came to America. ~\\

\indent Lastly, thank you to my family in both America and China for the support that you given me over the years.\\

\indent Sister Zhao Yue, you will always be in my memories. ~\\